---
title: "PMEs Fintech&Sustainability in Triveneto Area"
subtitle: "Demographic of respondents"
author: "Elisa Nardini"
date: "2024-02-02"
output: pdf_document
---

## Dataset and package reading

```{r setup, include=FALSE}
rm(list = ls())

# Set Wd ------------------------------------------------------------------------
setwd("~/Desktop/R/fintechsustainabilty")
df <- read.csv("dataset_demograph.csv")

# Packages ----------------------------------------------------------------------
library(ggplot2)
library(plotly)
library(tidyverse)

# Import Data -------------------------------------------------------------------
dataset_survey_demograph <- read.csv("dataset_demograph.csv")
#dataset_survey_demograph <- dataset_survey_demograph[, -c(1)]
```

Font settings

```{r}

# Packages ----------------------------------------------------------------------
library(extrafont)

# Import Font -------------------------------------------------------------------
font_import(pattern = "Arial")
loadfonts()

# Set Font ----------------------------------------------------------------------
par(family = "Arial") 
theme_set(theme_grey(base_family = "Arial"))
```
y

## EMPLOYEE EXPERTISE IN THE FIRM [X1]  --------------------------------------------------------------------------------------------------------------------------------

```{r}
#Expertise Stats ----------------------------------------------------------------
expertise_stats <- summary(dataset_survey_demograph[, 1])
print(expertise_stats)

# Saving ------------------------------------------------------------------------
# expertise_stats_df <- as.data.frame(t(expertise_stats))
# write.csv(expertise_stats_df, "expertise_stats.csv")
```


```{r, global=TRUE}

#Expertise Class Stats ----------------------------------------------------------
expertise_class_stats <- table(dataset_survey_demograph$X34)
print(expertise_class_stats)


# Total Percentage --------------------------------------------------------------
percent_expertise_class_stats <- prop.table(expertise_class_stats) * 100

# Combined
class_frequency_table <- data.frame(
  Frequency = expertise_class_stats,
  Percentage = percent_expertise_class_stats
)
print(class_frequency_table)

# Saving ------------------------------------------------------------------------
class_frequency_table_df <- as.data.frame(t(class_frequency_table))
write.csv(class_frequency_table_df, "class_frequency_table.csv")

```

Barplot Class Expertise

```{r}

# Increasing Order --------------------------------------------------------------
reorder_size <- function(x) {
        factor(x, levels = names(sort(table(x), increasing = TRUE)))
}

labels <- c("12%", "48%", "40%")

# Bar plot Class Expertise ------------------------------------------------------

Barplot_class_expertise <- ggplot(dataset_survey_demograph, aes(x =reorder_size(X34), fill = X34)) +
  geom_bar() +
  labs(title = NULL, x = "Expertise", y = "Frequency", fill = NULL) +
  theme(legend.position = "top") +
  scale_fill_manual(values = c("salmon", "darkolivegreen3", "darkturquoise"), labels = labels)
  #scale_x_discrete(labels = labels) 

print(Barplot_class_expertise)

ggsave(file.path("plot", "1.Barplot_class_expertise.pdf"), plot = Barplot_class_expertise)
```



## EMPLOYEE ROLE IN THE FIRM [X2]  -------------------------------------------------------------------------------------------------------------


```{r}
# Space Remove  -----------------------------------------------------------------
dataset_survey_demograph$X2 <- trimws(dataset_survey_demograph$X2, "both")

#Expertise Stats ----------------------------------------------------------------
role_freq <- table(dataset_survey_demograph[, 2])
print(role_freq)

# Saving ------------------------------------------------------------------------
# role_freq_df <- as.data.frame(t(role_freq))
# write.csv(role_freq_df, "role_freq.csv")
```

Barplot per Role

```{r}
# Decreasing Order --------------------------------------------------------------
reorder_size <- function(x) {
        factor(x, levels = names(sort(table(x), decreasing = TRUE)))
}

labels <- c("38%", "4%", "27%", "31%")

# Bar plot Role -----------------------------------------------------------------
BarPlot_role <- ggplot(dataset_survey_demograph, aes(x =reorder_size(X2), fill = X2)) +
  geom_bar() +
  labs(title = NULL, x = "Role", y = "Frequency", fill = NULL) +
    theme(axis.text.x = element_blank(),
        legend.position = "top", 
        text = element_text(size = 10)) +
    scale_fill_manual(values = c("salmon", "darkorchid1", "darkturquoise","darkolivegreen3"))+
    scale_x_discrete(labels = labels) 


print(BarPlot_role)
ggsave(file.path("plot", "2.BarPlot_role.pdf"), plot = BarPlot_role)
```

```{r}

#Role Stats ---------------------------------------------------------------------
role_stats <- table(dataset_survey_demograph[, 2])

# Total Percentage --------------------------------------------------------------
percent_role_stats <- prop.table(role_stats) * 100

role_frequency_table <- data.frame(
  Percentage = percent_role_stats
)
print(role_frequency_table)
```


```{r}
# Pie Chart 
PieChart_role <- ggplot(dataset_survey_demograph, aes(x = "", fill = X2)) +
  geom_bar(width = 1, color = "white", position = "fill") +
  coord_polar("y", start = 0) +
  labs(title = NULL, fill = NULL) +
  coord_polar(theta = "y") +
  theme_void() +
  theme(legend.position = "left", text = element_text(size = 14))
  

print(PieChart_role)
ggsave(file.path("plot", "2.PieChart_role.pdf"), plot = BarPlot_role)
```


## EMPLOYEE EXPERTISE IN THE SECTOR [X4]  --------------------------------------------------------------------------------------------------------------------------------

```{r}

#Expertise Stats ----------------------------------------------------------------
expertise_stats <- summary(dataset_survey_demograph[, 4])
print(expertise_stats)

# Saving ------------------------------------------------------------------------
# expertise_stats_df <- as.data.frame(t(expertise_stats))
# write.csv(expertise_stats_df, "expertise_stats.csv")
```


```{r, global=TRUE}

#Expertise Class Stats ----------------------------------------------------------
expertise_class_stats <- table(dataset_survey_demograph$X35)
print(expertise_class_stats)


# Total Percentage --------------------------------------------------------------
percent_expertise_class_stats <- prop.table(expertise_class_stats) * 100

# Combined
class_frequency_table <- data.frame(
  Frequency = expertise_class_stats,
  Percentage = percent_expertise_class_stats
)
print(class_frequency_table)


# Saving ------------------------------------------------------------------------
# class_frequency_table_df <- as.data.frame(t(class_frequency_table))
# write.csv(class_frequency_table_df, "class_frequency_table.csv")

```


Barplot Class Expertise in Sector

```{r}

# Increasing Order --------------------------------------------------------------
reorder_size <- function(x) {
        factor(x, levels = names(sort(table(x), increasing = TRUE)))
}

labels <- c("14%", "55%", "31%")

# Barplot
Barplot_class_expertise_sector <- ggplot(dataset_survey_demograph, aes(x = reorder_size(X35), fill = X35)) +
  geom_bar() +
  labs(title = NULL, x = "Expertise", y = "Frequency", fill = NULL) +
  theme(legend.position = "top") +
  scale_fill_manual(values = c("salmon", "darkolivegreen3", "darkturquoise"), labels = labels)

print(Barplot_class_expertise_sector)
ggsave(file.path("plot", "3.Barplot_class_expertise_sector.pdf"), plot = Barplot_class_expertise_sector)

```

## EMPLOYEE EXPERTISE + EXPERTISE IN THE SECTOR [X1; X4]  -------------------------------------------------------------------------

```{r}
# Increasing Order --------------------------------------------------------------
reorder_size <- function(x) {
        factor(x, levels = names(sort(table(x), increasing = FALSE)))
}

# Counts
counts <- dataset_survey_demograph[, 34:35] %>%
  gather(key = "colonna", value = "classe") %>%
  count(colonna, classe)

print(counts)

```

```{r}
# Bar Plot ----------------------------------------------------------------------
counts <- counts[order(counts_df$n), ]
counts$classe_ord <- factor(counts$classe, levels = c("<2", "2-10", ">10"))

# Bar Plot Expertise FIRM/SECTOR
BarPlot_firm_sector <- ggplot(counts, aes(x = classe_ord, y = n, fill = colonna)) +
  geom_bar(position = "dodge", stat = "identity") +
  labs(title = NULL,
       x = "Expertise",
       y = "Years",
       fill = NULL) +
  theme(legend.position = "top") +
  scale_fill_manual(values = c("salmon", "darkturquoise"), labels = labels)

print(BarPlot_firm_sector)


ggsave(file.path("plot", "4.BarPlot_firm_sector.pdf"), plot = BarPlot_firm_sector)

```



## EMPLOYEE EXPERTISE + ROLE [X34; X2]  --------------------------------------------------------------------------------------------------------------------------------

```{r}
table_Expertise_Role <- table(dataset_survey_demograph$X2, dataset_survey_demograph$X35)
print(table_Expertise_Role)
```


```{r}
Expertise_Role_df <- as.data.frame(table_Expertise_Role)
print(Expertise_Role_df)
```


```{r}

# Bar Plot
BarPlot_role_expertise <- ggplot(Expertise_Role_df, aes(x = Var1, y = Freq, fill = Var2)) +
  geom_bar(position="dodge2", stat="identity") +
  labs(title = NULL,
       x = "Area",
       y = "Experience distribution",
       fill = NULL) +
  theme(legend.position = "top") +
  scale_fill_manual(values = c("salmon", "darkturquoise","darkolivegreen3")) +
  theme(text = element_text(size = 10))


print(BarPlot_role_expertise)
ggsave(file.path("plot", "5.BarPlot_role_expertise.pdf"), plot = BarPlot_role_expertise)

```
```{r}

# Bar Plot
BarPlot_expertise_role <- ggplot(Expertise_Role_df, aes(x = Var2, y = Freq, fill = Var1)) +
  geom_bar(position="dodge2", stat="identity") +
  labs(title = NULL,
       x = "Experience",
       y = "Experience distribution",
       fill = NULL) +
  theme(legend.position = "top") +
  scale_fill_manual(values = c("salmon", "darkorchid1", "darkturquoise","darkolivegreen3")) +
  theme(text = element_text(size = 10))


print(BarPlot_expertise_role)
ggsave(file.path("plot", "5.BarPlot_expertise_role.pdf"), plot = BarPlot_expertise_role)

```


## FINTECH KNOWLEDGE [X5]  ---------------------------------------------------------------------------------------------------------------------------------

```{r}

#Expertise Stats ----------------------------------------------------------------
fintech_knowledge_stats <- table(dataset_survey_demograph[, 5])
print(fintech_knowledge_stats)

# Saving ------------------------------------------------------------------------
# fintech_knowledge_stats_df <- as.data.frame(t(fintech_knowledge_stats))
# write.csv(fintech_knowledge_stats_df, "fintech_knowledge_stats.csv")
```

BarPlot Fintech Knowledge

```{r}

BarPlot_fintech_knowledge <- ggplot(dataset_survey_demograph, aes(x = X5)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Values", y = "Frequency") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


print(BarPlot_fintech_knowledge)
#ggsave(file.path("plot", "6.BarPlot_fintech_knowledge.pdf"), plot = BarPlot_fintech_knowledge)

```


```{r}
# Density
dens <- density(dataset_survey_demograph$X5)

Densità_fintech_knowledge <- ggplot() +
  geom_line(data = data.frame(x = dens$x, y = dens$y), aes(x, y), color = "skyblue") +
  geom_polygon(data = data.frame(x = dens$x, y = dens$y), aes(x, y), fill = "skyblue") +
  labs(title = "", x = "Value", y = "Frequency") +
  theme(axis.ticks.x = element_blank())+
  theme(text = element_text(size = 10))

  
print(Densità_fintech_knowledge)
ggsave(file.path("plot", "6.Densità_fintech_knowledge.pdf"), plot = Densità_fintech_knowledge)

```


## FINTECH KNOWLEDGE AND ROLE [X5; X2]  --------------------------------------------------------------------------------------------------------------------------------

```{r}
#Fintech Knowledge per Role Stats ----------------------------------------------------------------
tabele_FK_Role <- table(dataset_survey_demograph$X2, dataset_survey_demograph$X5)
print(tabele_FK_Role)

# Saving ------------------------------------------------------------------------
# tabele_FK_Role_df <- as.data.frame(t(tabele_FK_Role))
# write.csv(tabele_FK_Role_df, "tabele_FK_Role.csv")
```

```{r}
media_condizionata <- aggregate(X5 ~ X2, data = dataset_survey_demograph, FUN = mean)
media_condizionata <- media_condizionata %>% arrange(X5)
media_condizionata$X2 <- factor(media_condizionata$X2, levels = media_condizionata$X2)
print(media_condizionata)
```

Fintech Knowledge per role Bar Plot  --------------------------------------------

```{r}
# Barplot Fintech Knowledge per role   ------------------------------------------
Barplot_FK_per_role <- ggplot(media_condizionata, aes(x = X2, y = X5, fill = X2)) +
  geom_bar(stat = "identity", width = 0.8) +
  scale_fill_viridis_d() +
  labs(title = NULL, x = "Area", y = "Mean Fintech Knowledge", fill = NULL) +
  theme(axis.text.x = element_blank())+
  theme(legend.position = "top", text = element_text(size = 10)) +
  scale_y_continuous(breaks = seq(0, 7, by = 1), limits = c(0, 7))  

print(Barplot_FK_per_role)

ggsave("Barplot_FK_per_role.pdf", plot = Barplot_FK_per_role)
ggsave(file.path("plot", "7.Barplot_FK_per_role.pdf"), plot = Barplot_FK_per_role)
```

Adding Weights ------------------------------------------------------------------

```{r}

media_condizionata <- aggregate(X5 ~ X2, data = dataset_survey_demograph, FUN = mean)
media_condizionata <- media_condizionata %>% arrange(X5)


total_freq <- sum(table(dataset_survey_demograph$X2))

media_condizionata <- media_condizionata %>%
  mutate(Peso = table(dataset_survey_demograph$X2)[as.character(X2)] / total_freq)

media_condizionata <- media_condizionata %>%
  mutate(Media_Pesata = X5 * Peso)

media_condizionata$X2 <- factor(media_condizionata$X2, levels = media_condizionata$X2)

print(media_condizionata)

```

```{r}
# Barplot Fintech Knowledge per role   ------------------------------------------

Barplot_FK_per_role_weight <- ggplot(media_condizionata, aes(x = X2, y = Media_Pesata, fill = X2)) +
  geom_bar(stat = "identity", width = 0.8) +
  scale_fill_viridis_d() +
  labs(title = NULL, x = "Area", y = "Mean Fintech Knowledge", fill = "Legend") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())+
  theme(legend.position = "top", text = element_text(size = 10)) +
  scale_y_continuous(breaks = seq(0, 3, by = 1), limits = c(0, 3))  

print(Barplot_FK_per_role_weight)


ggsave(file.path("plot", "7.Barplot_FK_per_role_weight.pdf"), plot = Barplot_FK_per_role_weight)

```

## HORIZONTALS KNOWLEDGE AND ROLE [HORIZONTALS; X2]  --------------------------------------------------------------------------------------------------------------------------------

```{r}

# HORIZONTALS RATIO

# Total "Si" (Yes) response in columns 6 - 8, 13, 14
total_si <- rowSums(dataset_survey_demograph[, c(6, 7, 8, 13, 14)] == "Si", na.rm = TRUE)

# Normalize values from 0 to 1
min_val <- min(total_si)
max_val <- max(total_si)
normalized_val <- (total_si - min_val) / (max_val - min_val)

# Add new column for Horizontal Ratio
dataset_survey_demograph$horizontals <- normalized_val
```

```{r}
tabele_FK_Role <- table(dataset_survey_demograph$X2, dataset_survey_demograph$horizontals)
print(tabele_FK_Role)
```

```{r}
media_condizionata <- aggregate(horizontals ~ X2, data = dataset_survey_demograph, FUN = mean)
print(media_condizionata)
media_condizionata <- media_condizionata %>% arrange(horizontals)
media_condizionata$X2 <- factor(media_condizionata$X2, levels = media_condizionata$X2)
```

```{r}
# Barplot
Barplot_horizontals_per_role <- ggplot(media_condizionata, aes(x = X2, y = horizontals, fill = X2)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis_d() +
  labs(title = NULL, x = "Area", y = "Mean Fintech Knowledge Horizontals", fill = NULL) +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())+
  theme(legend.position = "top", text = element_text(size = 10))

print(Barplot_horizontals_per_role)

ggsave(file.path("plot", "8.Barplot_horizontals_per_role.pdf"), plot = Barplot_horizontals_per_role)

```

## VERTICALS KNOWLEDGE AND ROLE [VERTICALS; X2]  --------------------------------------------------------------------------------------------------------------------------------

```{r}

# VERTICALS RATIO

# Total "Si" (Yes) response in columns 9 - 12
total_si <- rowSums(dataset_survey_demograph[, 9:12] == "Si", na.rm = TRUE)

# Normalize values from 0 to 1
min_val <- min(total_si)
max_val <- max(total_si)
normalized_val <- (total_si - min_val) / (max_val - min_val)

# Add new column for Horizontal Ratio
dataset_survey_demograph$verticals <- normalized_val
```

```{r}

tabele_FK_expertise <- table(dataset_survey_demograph$X2, dataset_survey_demograph$verticals)
print(tabele_FK_expertise)
```

```{r}
media_condizionata <- aggregate(verticals ~ X2, data = dataset_survey_demograph, FUN = mean)
print(media_condizionata)
media_condizionata <- media_condizionata %>% arrange(verticals)
media_condizionata$X2 <- factor(media_condizionata$X2, levels = media_condizionata$X2)
```

```{r}
# Barplot
Barplot_verticals_per_role <- ggplot(media_condizionata, aes(x = X2, y = verticals, fill = X2)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis_d() +
  labs(title = NULL, x = "Area", y = "Mean Fintech Verticals Knowledge", fill = NULL) +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())+ 
  theme(legend.position = "top", text = element_text(size = 10))
print(Barplot_verticals_per_role)


ggsave(file.path("plot", "9.Barplot_verticals_per_role.pdf"), plot = Barplot_verticals_per_role)

```


## FINTECH KNOWLEDGE AND SECTOR [X5; X3]  --------------------------------------------------------------------------------------------------------------------------------

```{r}
# Space Remove  -----------------------------------------------------------------
dataset_survey_demograph$X2 <- trimws(dataset_survey_demograph$X2, "both")

# Frequency Table  --------------------------------------------------------------
tabele_FK_sector <- table(dataset_survey_demograph$X3, dataset_survey_demograph$X5)
print(tabele_FK_sector)
```

```{r}
media_condizionata <- aggregate(X5 ~ X3, data = dataset_survey_demograph, FUN = mean)
print(media_condizionata)
media_condizionata <- media_condizionata %>% arrange(X5)
media_condizionata$X3 <- factor(media_condizionata$X3, levels = media_condizionata$X3)
```

```{r}
# Pie Chart FK per Sector

Piechart_FK_per_sector <- ggplot(media_condizionata, aes(x = "", y = X5, fill = X3)) +
  geom_bar(stat = "identity") +
  coord_polar("y", start = 0) +
  scale_fill_viridis_d() +
  labs(title = NULL, x = NULL, y = NULL, fill = NULL) +
  theme_void() +
  theme(legend.position = "left", text = element_text(size = 10))

print(Piechart_FK_per_sector)

ggsave(file.path("plot", "10.Piechart_FK_per_sector.pdf"), plot = Piechart_FK_per_sector)



```


## FINTECH KNOWLEDGE AND EXPERTISE IN THE SECTOR [X5; X35] ---------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_FK_sector_expertise <- table(dataset_survey_demograph$X34, dataset_survey_demograph$X5)
print(tabele_FK_sector_expertise)
```

```{r}
media_condizionata <- aggregate(X5 ~ X34, data = dataset_survey_demograph, FUN = mean)
print(media_condizionata)
media_condizionata <- media_condizionata %>% arrange(X5)
media_condizionata$X34 <- factor(media_condizionata$X34, levels = media_condizionata$X34)
```

```{r}
# Barplot FK and Expertise in Firm

Barplot_FK_per_sector_expertise<- ggplot(media_condizionata, aes(x = X34, y = X5, fill = X34)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis_d() +
  labs(title = NULL, x = NULL, y = "Mean Fintech Knowledge", fill = NULL) +
  theme(axis.text.x = element_blank())+
  theme(legend.position = "top", text = element_text(size = 12))
  scale_y_continuous(breaks = seq(0, 7, by = 1), limits = c(0, 7)) 


print(Barplot_FK_per_sector_expertise)

ggsave(file.path("plot", "11.Barplot_FK_per_sector_expertise.pdf"), plot = Barplot_FK_per_sector_expertise)
```


## BLOCKCHAIN KNOWLEDGE [X6]  --------------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_blockchain <- table(dataset_survey_demograph[ ,6])
print(tabele_blockchain)
```

```{r}
# BarPlot
BarPlot_blockchain <- ggplot(dataset_survey_demograph, aes(x = X6)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Valori", y = "Frequenza") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_blockchain)
# ggsave("BarPlot_blockchain.pdf", plot = BarPlot_blockchain)
```



## AI KNOWLEDGE [X7] -----------------------------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_ai <- table(dataset_survey_demograph[ ,7])
print(tabele_ai)
```

```{r}
# BarPlot
BarPlot_ai <- ggplot(dataset_survey_demograph, aes(x = X7)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Valori", y = "Frequenza") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_ai)
# ggsave("BarPlot_ai.pdf", plot = BarPlot_ai)

```


## ML KNOWLEDGE [X8]  ] -----------------------------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_ml <- table(dataset_survey_demograph[ ,8])
print(tabele_ml)
```

```{r}
# BarPlot
BarPlot_ml <- ggplot(dataset_survey_demograph, aes(x = X8)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Valori", y = "Frequenza") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_ml)
# ggsave("BarPlot_ml.pdf", plot = BarPlot_ml)

```

## Crowfunding KNOWLEDGE [X9] -----------------------------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_crowfunding <- table(dataset_survey_demograph[ ,9])
print(tabele_crowfunding)
```

```{r}
# BarPlot
BarPlot_crowfunding <- ggplot(dataset_survey_demograph, aes(x = X9)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Valori", y = "Frequenza") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_ml)
# ggsave("BarPlot_crowfunding.pdf", plot = BarPlot_crowfunding)

```

## Peer to Peer KNOWLEDGE [X10]  -----------------------------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_p2p <- table(dataset_survey_demograph[ ,10])
print(tabele_p2p)
```

```{r}
# BarPlot
BarPlot_p2p <- ggplot(dataset_survey_demograph, aes(x = X9)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Valori", y = "Frequenza") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_p2p)
# ggsave("BarPlot_p2p.pdf", plot = BarPlot_p2p)
```

## Mobile Payment KNOWLEDGE [X11]  ------------------------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_mobilepay <- table(dataset_survey_demograph[ ,11])
print(tabele_mobilepay)
```

```{r}
# BarPlot
BarPlot_mobilepay <- ggplot(dataset_survey_demograph, aes(x = X11)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Valori", y = "Frequenza") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_mobilepay)
# ggsave("BarPlot_mobilepay.pdf", plot = BarPlot_mobilepay)
```

## NFT KNOWLEDGE [X12]  ------------------------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_nft <- table(dataset_survey_demograph[ ,12])
print(tabele_nft)
```

```{r}
# BarPlot
BarPlot_nft <- ggplot(dataset_survey_demograph, aes(x = X12)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Valori", y = "Frequenza") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_nft)
# ggsave("BarPlot_nft.pdf", plot = BarPlot_nft)
```


## Chatbot KNOWLEDGE [X13]  -------------------------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_chatbot <- table(dataset_survey_demograph[ ,13])
print(tabele_chatbot)
```

```{r}
# BarPlot
BarPlot_chatbot <- ggplot(dataset_survey_demograph, aes(x = X13)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Valori", y = "Frequenza") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_chatbot)
# ggsave("BarPlot_chatbot.pdf", plot = BarPlot_chatbot)
```


## Robotic Process Automation [X14]  -----------------------------------------------------------------------------------------------------------------------------------------

```{r}
tabele_chatbot <- table(dataset_survey_demograph[ ,14])
print(tabele_chatbot)
```

```{r}
# BarPlot
BarPlot_rba <- ggplot(dataset_survey_demograph, aes(x = X14)) +
  geom_bar(fill = "skyblue") +
  labs(x = "Valori", y = "Frequenza") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_rba)
# ggsave("BarPlot_rba.pdf", plot = BarPlot_rba)
```


## FINTECH OVERALL KNOWLEDGE [X6, X14]  -----------------------------------------------------------------------------------------------------------------------------------------

```{r}

# Counts
counts <- dataset_survey_demograph[, 6:14] %>%
  gather(key = "colonna", value = "risposta") %>%
  count(colonna, risposta)

counts$colonna <- factor(counts$colonna, levels = colnames(dataset_survey_demograph)[6:14])

labels <- c("Blockchain", "AI", "ML", "Crowfunding", "P2P", "Mobile payment ","NFT", "Chatbot", "RBA")

# Bar Plot
BarPlot_count <- ggplot(counts, aes(x = colonna, y = n, fill = risposta)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = NULL,
       x = "Fintech Instrument",
       y = "Count", fill = NULL) +
  theme_minimal()+
  theme(legend.position = "top", text = element_text(size = 12))+
  scale_x_discrete(labels = labels) 


print(BarPlot_count)
ggsave("BarPlot_count.pdf", plot = BarPlot_count)
```