---
title: "SMEs Fintech&Sustainability in Triveneto Area"
subtitle: "Sector Analysis"
author: "Elisa Nardini"
date: "2024-02-02"
output: pdf_document
---

## Dataset and package reading

```{r setup, include=FALSE}
rm(list = ls())

# Set Wd ------------------------------------------------------------------------
setwd("~/Desktop/R/fintechsustainabilty")
df <- read.csv("dataset_en.csv")

# Packages ----------------------------------------------------------------------
library(ggplot2)
library(plotly)
library(tidyverse)
library(dplyr)

# Import Data -------------------------------------------------------------------
dataset_survey_sector <- read.csv("dataset_en.csv")
dataset_survey_sector <- dataset_survey_sector[, -c(1)]
```

Font settings

```{r}

# Packages ----------------------------------------------------------------------
library(extrafont)

# Import Font -------------------------------------------------------------------
font_import(pattern = "Arial")
loadfonts()

# Set Font ----------------------------------------------------------------------
par(family = "Arial") 
theme_set(theme_grey(base_family = "Arial"))
```


## SECTOR STATS [X3]  -----------------------------------------------------------

```{r}

# Space remove ------------------------------------------------------------------
dataset_survey_sector$X3 <- trimws(dataset_survey_sector$X3, "both")

#Frequency Distribution ---------------------------------------------------------
sector_frequency <- table(dataset_survey_sector[, 3])

sector_frequency_df <- as.data.frame(sector_frequency)
sector_frequency_df <- sector_frequency_df[order(sector_frequency_df$Freq), ]
print(sector_frequency_df)

# Saving ------------------------------------------------------------------------
# sector_frequency_df <- as.data.frame(t(sector_frequency))
# write.csv(sector_frequency_df, "sector_frequency_df.csv")
```

Sector Variable Bar Plot  -------------------------------------------------------

```{r}

# Bar plot  ---------------------------------------------------------------------
BarPlot_Sectors <- ggplot(dataset_survey_sector, aes(x = X3, fill = X3)) +
  geom_bar() +
  labs(title = NULL, x = NULL, y = "Frequency", fill = NULL) +  
  theme(axis.text.x = element_blank()) +  
  scale_fill_viridis_d() 

print(BarPlot_Sectors)


ggsave(file.path("plot", "1.BarPlot_Sectors.pdf"), plot = BarPlot_Sectors)
```

Sector Variable Pie Chart  ------------------------------------------------------

```{r}
# Pie Chart  --------------------------------------------------------------------
PieChart_Sector <- ggplot(dataset_survey_sector, aes(x = "", fill = X3)) +
  geom_bar(width = 0.2, color = "white", position = "fill") +
  coord_polar("y", start = 0) +
  labs(title = NULL, 
       fill = NULL) +
  coord_polar(theta = "y") +
  scale_fill_discrete(name = NULL) +
  theme_void()
print(PieChart_Sector)
# ggsave("PieChart_Sector.pdf", plot = PieChart_Sector)
```



## FINTECH ADOPTION STATS [X15]  ------------------------------------------------


```{r}
# Frequency Distribution  -------------------------------------------------------
FA_frequency <- table(dataset_survey_sector[, 15])
print(FA_frequency)

# Saving ------------------------------------------------------------------------
# FA_frequency_df <- as.data.frame(t(FA_frequency))
# write.csv(FA_frequency_df, "FA_frequency.csv")
```

Fintech Adoption Bar Plot  ------------------------------------------------------

```{r}
# Bar plot  ---------------------------------------------------------------------
BarPlot_FA <- ggplot(dataset_survey_sector, aes(x = X15)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Fintech Adoption", x = "Response", y = "Frequency") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


print(BarPlot_FA)
# ggsave("BarPlot_FA.pdf", plot = BarPlot_FA)
```





## FINTECH ADOPTION STATS PER SECTOR [X3; X15]  ---------------------------------

```{r}

tabella_sector_FA <- table(dataset_survey_sector$X3, dataset_survey_sector$X15)
print(tabella_sector_FA)

# Saving ------------------------------------------------------------------------
# tabella_sector_FA_df <- as.data.frame(t(tabella_sector_FA))
# write.csv(tabella_sector_FA_df, "tabella_sector_FA.csv")
```


Fintech Adoption per sector Bar Plot  -------------------------------------------

```{r}
# Barplot
Barplot_FA_per_Sector <- ggplot(dataset_survey_sector, aes(x = X3, y = X15, fill = X3)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_viridis_d() +
  labs(title = NULL, x = NULL, y = "Response", fill = "Legend") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) 

print(Barplot_FA_per_Sector)


# ggsave("Barplot_FA_per_Sector.pdf", plot = Barplot_FA_per_Sector)
```

## FINTECH/SUSTAINABILITY PROJECTS STATS PER SECTOR  ---------------------------- 


```{r}
#Frequency Distribution ---------------------------------------------------------
frequency_projects <- table(dataset_survey_sector[, 16])
print(frequency_projects)

# Saving ------------------------------------------------------------------------
# frequency_projects_df <- as.data.frame(t(frequency_projects))
# write.csv(frequency_projects_df, "frequency_projects.csv")
```

Bar Plot Projects  --------------------------------------------------------------

```{r}
df_X16_filtered <- dataset_survey_sector[dataset_survey_sector$X16 != 0, ] 

# BarPlot
BarPlot_projects <- ggplot(df_X16_filtered, aes(x = X16)) +
  geom_bar(fill = "skyblue") +
  labs(title = NULL, x = "Projects", y = "Frequency") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(BarPlot_projects)
# ggsave("BarPlot_projects.pdf", plot = BarPlot_projects)
```


## FINTECH/SUSTAINABILITY PROJECTS STATS per Sector [X3; X16]  -----------------------------


```{r}
#Frequency Table
table_sector_Projects <- table(dataset_survey_sector$X3, dataset_survey_sector$X16)
print(table_sector_Projects)

# Saving ------------------------------------------------------------------------
# table_sector_Projects_df <- as.data.frame(t(table_sector_Projects))
# write.csv(table_sector_Projects_df, "table_sector_Projects.csv")
```



## Applicability issues [x33] ---------------------------------------------------

```{r}
#Frequency Distribution ---------------------------------------------------------
issues_frequency <- table(dataset_survey_sector[, 33])
print(issues_frequency)

# Saving ------------------------------------------------------------------------
# issues_frequency_df <- as.data.frame(t(issues_frequency))
# write.csv(issues_frequency_df, "issues_frequency.csv")
```

Applicability issues Variable Bar Plot  -----------------------------------------

```{r}
# Bar plot  ---------------------------------------------------------------------
BarPlot_issues <- ggplot(dataset_survey_sector, aes(x = X33, fill = X33)) +
  geom_bar() +
  labs(title = "Problems", x = NULL, y = "Frequency") +  
  theme(axis.text.x = element_blank()) +  
  scale_fill_discrete(name = "Legend")

print(BarPlot_issues)
# ggsave("BarPlot_issues.pdf", plot = BarPlot_issues)
```

## SECTOR AND Applicability issues  ---------------------------------------------


```{r}
#Frequency Table
table_sector_problems <- table(dataset_survey_sector$X3, dataset_survey_sector$X33)
print(table_sector_problems)

# Saving ------------------------------------------------------------------------
# table_sector_problems_df <- as.data.frame(t(table_sector_problems))
# write.csv(table_sector_problems_df, "table_sector_problems.csv")

```



## VERTICALS KNOWLEDGE [X34] ----------------------------------------------------

```{r}

# VERTICALS RATIO

# Total "Si" (Yes) response in columns 9 - 12
total_si <- rowSums(dataset_survey_sector[, 9:12] == "Si", na.rm = TRUE)

# Normalize values from 0 to 1
min_val <- min(total_si)
max_val <- max(total_si)
normalized_val <- (total_si - min_val) / (max_val - min_val)

# Add new column for Horizontal Ratio
dataset_survey_sector$X34 <- normalized_val
```

```{r}
#Frequency Distribution ---------------------------------------------------------
vertical_ratio_frequency <- summary(dataset_survey_sector[, 34])
print(vertical_ratio_frequency)

# Saving ------------------------------------------------------------------------
# vertical_ratio_frequency_df <- as.data.frame(t(vertical_ratio_frequency))
# write.csv(vertical_ratio_frequency_df, "vertical_ratio_frequency.csv")
```

Verticals density plot  ---------------------------------------------------------

```{r}
# Density plot  -----------------------------------------------------------------
dens <- density(dataset_survey_sector$X34)

density_verticals <- ggplot() +
  geom_line(data = data.frame(x = dens$x, y = dens$y), aes(x, y), color = "skyblue") +
  geom_polygon(data = data.frame(x = dens$x, y = dens$y), aes(x, y), fill = "lightblue") +
  labs(title = "", x = "Value", y = "Density") +
  theme_minimal()
print(density_verticals)

# ggsave("density_verticals.pdf", plot = density_verticals)
```


## SECTOR AND VERTICALS KNOWLEDGE -----------------------------------------------


```{r}

#Frequency Table ----------------------------------------------------------------
table_sector_verticals <- table(dataset_survey_sector$X3, dataset_survey_sector$X34)
print(table_sector_verticals)

# Saving ------------------------------------------------------------------------
# table_sector_verticals_df <- as.data.frame(t(table_sector_verticals))
# write.csv(table_sector_verticals_df, "table_sector_verticals.csv")
```

Conditionate mean ---------------------------------------------------------------

```{r}

media_condizionata <- aggregate(X34 ~ X3, data = dataset_survey_sector, FUN = mean)
print(media_condizionata)
media_condizionata <- media_condizionata %>% arrange(X34)
media_condizionata$X3 <- factor(media_condizionata$X3, levels = media_condizionata$X3)
```

```{r}
# Barplot
Barplot_verticals_sector <- ggplot(media_condizionata, aes(x = X3, y = X34, fill = X3)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis_d() +
  labs(title = NULL, x = NULL, y = "Verticals Ratio", fill = "Legend") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) 

print(Barplot_verticals_sector)

# ggsave("Barplot_verticals_sector.pdf", plot = Barplot_verticals_sector)

```


## HORIZONTALS KNOWLEDGE [X35]  -------------------------------------------------


```{r}

# HORIZONTALS RATIO

# Total "Si" (Yes) response in columns 6 - 8, 13, 14
total_si <- rowSums(dataset_survey_sector[, c(6, 7, 8, 13, 14)] == "Si", na.rm = TRUE)

# Normalize values from 0 to 1
min_val <- min(total_si)
max_val <- max(total_si)
normalized_val <- (total_si - min_val) / (max_val - min_val)

# Add new column for Horizontal Ratio
dataset_survey_sector$X35 <- normalized_val
```

```{r}
#Frequency Distribution ---------------------------------------------------------
horizontals_ratio_frequency <- summary(dataset_survey_sector[, 35])
print(horizontals_ratio_frequency)

# Saving ------------------------------------------------------------------------
# horizontals_ratio_frequency_df <- as.data.frame(t(horizontals_ratio_frequency))
# write.csv(horizontals_ratio_frequency_df, "horizontals_ratio_frequency.csv")
```

Verticals density plot  ---------------------------------------------------------

```{r}
# Density plot  -----------------------------------------------------------------
dens <- density(dataset_survey_sector$X35)

density_horizontals <- ggplot() +
  geom_line(data = data.frame(x = dens$x, y = dens$y), aes(x, y), color = "skyblue") +
  geom_polygon(data = data.frame(x = dens$x, y = dens$y), aes(x, y), fill = "lightblue") +
  labs(title = "", x = "Value", y = "Density") +
  theme_minimal()
print(density_horizontals)

# ggsave("density_horizontals.pdf", plot = density_horizontals)
```


## SECTOR AND HORIZONTALS KNOWLEDGE  ----------------------------------------------

```{r}

#Frequency Table ----------------------------------------------------------------
table_sector_horizontals <- table(dataset_survey_sector$X3, dataset_survey_sector$X35)
print(table_sector_horizontals)

# Saving ------------------------------------------------------------------------
# table_sector_horizontals_df <- as.data.frame(t(table_sector_horizontals))
# write.csv(table_sector_horizontals_df, "table_sector_horizontals.csv")
```

Conditionate mean ---------------------------------------------------------------

```{r}

media_condizionata <- aggregate(X35 ~ X3, data = dataset_survey_sector, FUN = mean)
print(media_condizionata)
media_condizionata <- media_condizionata %>% arrange(X35)
media_condizionata$X3 <- factor(media_condizionata$X3, levels = media_condizionata$X3)
```


```{r}
# Barplot
Barplot_horizontals_sector <- ggplot(media_condizionata, aes(x = X3, y = X35, fill = X3)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis_d() +
  labs(title = NULL, x = NULL, y = "Verticals Ratio", fill = "Legend") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) 

print(Barplot_horizontals_sector)

# ggsave("Barplot_horizontals_sector.pdf", plot = Barplot_horizontals_sector)

```



